\vspace{-2em}The 4th Workshop on Sustainable Software for Science: Best Practices and Experiences (WSSSPE4)

### 2016-06-11 WSSSPE4_proposal/WSSSPE4_proposal.tex
some work in assessment

\textcolor{red}{How will we know if this is successful? - for track 2, survey attendees?  for track 1, see if we have proposals submitted or activities underway six months later?}

>>>>

We will assess the success of WSSSPE4 with two different mechanisms.
For Track 1, the activities and\slash or deliverables proposed during the workshop (and documented in the report) will be evaluated for progress or completion six months following the workshop.
This could include submission of proposals or papers, or the creation of other useful products (e.g., tutorials, wiki, forum).
Track 2 activities will be assessed by surveying attendees following the workshop with questions such as ``What software development practices are you aware of now that you were not aware of prior to WSSSPE4?'' and ``What practices do you intend on implementing in your own software development work following WSSSPE4?''.
In addition, the submission of a workshop report for peer review within six months will be another metric for success.

\textcolor{red}{How will we know if this is successful? - for track 2, survey attendees?  for track 1, see if we have proposals submitted or activities underway six months later?}
\textcolor{blue}{I tried fleshing those suggestions about a bit; what about assessment of efforts to get people from underrepresented groups involved?}
